---
title: "R Notebook"
output: html_notebook
---


## Bar Chart term
Bar chart are effective for visualizing and comparing data across different categories, here the height of each bar is proportional to the value or frequency it represents

## Drawing a bar chart
to draw a bar chart you will need only a categorical variable given to the x aesthetics
```{r}
diamonds |> ggplot(aes(x = cut)) + geom_bar()
```
## flipping the bar chart
to flip the bars, assign the categorical variable to y aesthetics 
```{r}
diamonds |> ggplot(aes(y = cut)) + geom_bar()
```
or similarly
```{r}
diamonds |> ggplot(aes(x = cut)) + geom_bar() + coord_flip()
```
## Adding colours(path)
to add color to bar chart path drawn add the color argument **NOT THE AESTHETICS FUNCTION COLOR**
```{r}
diamonds |> ggplot(aes(x = cut)) + geom_bar(color = "blue")
```
## Adding colours(fill)
to add color to bar chart filling everything with the same color, add the color argument **NOT THE AESTHETICS FUNCTION COLOR**
```{r}
diamonds |> ggplot(aes(x = cut)) + geom_bar(fill = "blue")
```
## Adding unique Colour
to add unique color to each bar, use the fill argument **IN THE AESTHETICS FUNCTION** mapping it to a variable
```{r}
diamonds |> ggplot(aes(x = cut)) + geom_bar(mapping = aes(fill = cut))
```
## Adding unique Colour(specific)
to add unique color to a specific bar, use scale_fill_manual function to manually add the colors, name the colors for more specificity
**Note** you will need to add fill in the aesthetics for things to work, map the fill in the aesthetics to a variable
```{r}
bar_colors <- c("red","blue","black","green","brown")
names(bar_colors) <- unique(diamonds$cut)
diamonds |> ggplot(aes(x = cut, fill = cut)) + geom_bar() + scale_fill_manual(values = bar_colors)
```
## Component(stacked) bar chart
showing proportion of groups within a group in a group
this displays the total value while also showing the contribution of each individual subcategories.

## Adding stacked bar chart
after adding a normal bar chart add the fill to another different variable which is the groups within a particular, and set the position argument **NOT THE AES FUNCTION** and set it to position_stack() 
we can use in sense of a progress bar

if you flip the coordinate set reverse to true inside the postion_stack()
```{r}
diamonds |> ggplot(aes(x = cut)) + geom_bar(mapping = aes(fill = clarity), position = position_stack())
```
## Adding multiple barchart
for multiple bar chart change the above bar chart(stacked), change the position argument to position_dodge
```{r}
diamonds |> ggplot(aes(x = cut)) + geom_bar(mapping = aes(fill = clarity), position = position_dodge())
```










